---
title: "Market Segmentation"
output:
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```
```{r data}
library(ggplot2)
library(LICORS)  # for kmeans++
library(foreach)
library(mosaic)

social = read.csv('http://raw.githubusercontent.com/jgscott/STA380/master/data/social_marketing.csv', header=TRUE)
head(social[,-1],5)

#scale the data
X = social[,-1]
X = X/rowSums(X)
```

We decided to scale the data according to their row sums because we want all users' interests to be equally weighted regardless of their overall level of twitter usage.


#Kmeans method:
```{r kmeans method}
#test various k values
CH_list = {}
kval = c(2,4,6,10,15)
for (i in kval){
  # Using kmeans++ initialization
  cluster = kmeanspp(X, k=i, nstart=25)
  W = cluster$tot.withinss
  B = cluster$betweenss
  nk = (nrow(social)-i)/(i-1)
  val = (B/W)*nk
  CH_list = c(CH_list,val)
  cat(c(i," "))
}

#plot CH index againt k value to find best k
plot(kval,CH_list)
```

The plot of CH index against K value, we decided that the best k value is 6. The max CH value occurs when k = 2, but since our dataset is so large, it makes sense to split into more than 2 clusters. At a k value of 6, the CH index is high, but we are clustering the data into smaller subsets, so we chose to work with k = 6 clusters.

```{r}
#run kmeans to cluster the data
set.seed(11)
finalcluster = kmeanspp(X, k=6, nstart=25)

finalcluster$size
finalcluster$centers[2,]
finalcluster$centers[4,]
```

The largest clusters are clusters 2 and 4, so we can look at the top topics of interest in the clusters to learn about many of the followers. Cluster 2 displays an interest in photo sharing, shopping, current events, and travel. Cluster 4 shows interest in sports fandom, food, and religion. We can use this information to tailor our message in our marketing campaign.

```{r}
#plot to show our target influencers
qplot(health_nutrition, food, data=X, color=factor(finalcluster$cluster))
```

After looking at the 6 clusters, we plotted the clusters against health_nutrition and food because we determined that these are the topics that most relate to nutrientH2O. We found that groups 4 and 5 show a high level of interest in these topics, so we can find the influencers among these groups to help us campaign about NutrientH2O.


#PCA method:
```{r PCA method}

# PCA
set.seed(12)
PC = prcomp(X, scale=TRUE)
loadings = PC$rotation
scores = PC$x


# Show the top topics associated with each component
o1 = order(loadings[,1], decreasing = TRUE)
colnames(X)[head(o1,6)]
colnames(X)[tail(o1,6)]

o2 = order(loadings[,2], decreasing = TRUE)
colnames(X)[head(o2,6)]
colnames(X)[tail(o2,6)]

#plot the data on PC1 and PC2
qplot(scores[,1], scores[,2], xlab='Component 1', ylab='Component 2')
#plot all vectors
biplot(PC)
```

Because health_nutrition is the lowest loading in PC2 and food is high in PC1, we want to target the users whose PC2 is low and PC1 is high. These users are plotted in the bottom region slightly to the right in the biplot shown.


